Supplementary materials for 'Openness and computational reproducibility in plant pathology: where do we stand and a way forward

### 2022-07-08 analysis/paper/supplementary_materials.Rmd
Remove supplementary materials and put in own file for item numbering

---
title: "Supplementary Materials for 'Openness and computational reproducibility in plant pathology: where do we stand and a way forward'"
author:
  - Adam H. Sparks:
      email: Adam.Sparks@dpird.wa.gov.au
      institute: DPIRD, USQ
      correspondence: true
  - Emerson M. Del Ponte:
      institute: UFV
  - Kaique S. Alves:
      institute: UFV
  - Zachary S. L. Foster:
      institute: OSU
  - Niklaus J. Grünwald:
      institute: ARS
institute:
  - DPIRD: Department of Primary Industries and Regional Development, Farming Systems Innovation, Perth WA 6000, Australia
  - USQ: University of Southern Queensland, Centre for Crop Health, Toowoomba Qld 4350, Australia
  - UFV: Departmento de Fitopatologia, Universidade Federal de Viçosa, Brazil
  - OSU: Department of Botany and Plant Pathology, Oregon State University, Corvallis OR 97331, USA
  - ARS: Horticultural Crops Research Unit, USDA Agricultural Research Service, Corvallis OR 97330, USA
output: 
  bookdown::word_document2:
     fig_caption: yes
     number_sections: FALSE
     reference_docx: "../templates/phytopath_template.docx"
     pandoc_args:
       - '--lua-filter=scholarly-metadata.lua'
       - '--lua-filter=author-info-blocks.lua'
       - '--lua-filter=pagebreak.lua'
---

```{r, setup, echo=FALSE, message=FALSE, warning=FALSE}

library("Reproducibility.in.Plant.Pathology")
packages <- c(
  "tidyverse",
  "bayesplot",
  "bayestestR",
  "brms",
  "extrafont",
  "flextable",
  "grDevices",
  "ggpubr",
  "here",
  "knitr",
  "officer",
  "pander",
  "parameters",
  "posterior",
  "report",
  "tools"
)

@@

opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  out.width = "100%",
  comment = "#>",
  dev = "cairo_ps",
  cache = FALSE
)

@@

load(
  system.file(
    "extdata",
    "m_h1.Rda",
    package = "Reproducibility.in.Plant.Pathology",
    mustWork = TRUE
  )
)
load(
  system.file(
    "extdata",
    "m_h1_report.Rda",
    package = "Reproducibility.in.Plant.Pathology",
    mustWork = TRUE
  )
)
load(
  system.file(
    "extdata",
    "m_h2.Rda",
    package = "Reproducibility.in.Plant.Pathology",
    mustWork = TRUE
  )
)
load(
  system.file(
    "extdata",
    "m_h2_report.Rda",
    package = "Reproducibility.in.Plant.Pathology",
    mustWork = TRUE
  )
)

knitr::opts_chunk$set(
  fig.cap.pre = "Figure S",
  tab.cap.pre = "Table S"
)

```

@@

font_import()
```

>>>>

---
title: "Supplementary materials for 'Openness and computational reproducibility in plant pathology: where do we stand and a way forward'"
author:
  - Adam H. Sparks:
      email: Adam.Sparks@dpird.wa.gov.au
      institute: DPIRD, USQ
      correspondence: true
  - Emerson M. Del Ponte:
      institute: UFV
  - Kaique S. Alves:
      institute: UFV
  - Zachary S. L. Foster:
      institute: OSU
  - Niklaus J. Grünwald:
      institute: ARS
institute:
  - DPIRD: Department of Primary Industries and Regional Development, Farming Systems Innovation, Perth WA 6000, Australia
  - USQ: University of Southern Queensland, Centre for Crop Health, Toowoomba Qld 4350, Australia
  - UFV: Departmento de Fitopatologia, Universidade Federal de Viçosa, Brazil
  - OSU: Department of Botany and Plant Pathology, Oregon State University, Corvallis OR 97331, USA
  - ARS: Horticultural Crops Research Unit, USDA Agricultural Research Service, Corvallis OR 97330, USA
output: 
  bookdown::word_document2:
     fig_caption: yes
     number_sections: FALSE
     reference_docx: "../templates/phytopath_template.docx"
     pandoc_args:
       - '--lua-filter=scholarly-metadata.lua'
       - '--lua-filter=author-info-blocks.lua'
       - '--lua-filter=pagebreak.lua'
bibliography: references.bib
link-citations: no
csl: "../templates/american-phytopathological-society.csl"
---

```{r, setup, echo=FALSE, message=FALSE}
packages <- c(
  "DiagrammeR",
  "DiagrammeRsvg",
  "bayesplot",
  "bayestestR",
  "brms",
  "dplyr",
  "english",
  "extrafont",
  "flextable",
  "ggpubr",
  "grDevices",
  "here",
  "janitor",
  "knitr",
  "officer",
  "parameters",
  "patchwork",
  "posterior",
  "report",
  "rsvg",
  "tidyr",
  "tools"
)

@@

opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  out.width = "100%",
  comment = "#>",
  dev = "cairo_ps",
  cache = FALSE,
  fig.cap.pre = "Figure S",
  tab.cap.pre = "Table S"
)

@@

load(
  system.file(
    "extdata",
    "m_h1.Rda",
    package = "Reproducibility.in.Plant.Pathology",
    mustWork = TRUE
  )
)
load(
  system.file(
    "extdata",
    "m_h1_report.Rda",
    package = "Reproducibility.in.Plant.Pathology",
    mustWork = TRUE
  )
)
load(
  system.file(
    "extdata",
    "m_h2.Rda",
    package = "Reproducibility.in.Plant.Pathology",
    mustWork = TRUE
  )
)
load(
  system.file(
    "extdata",
    "m_h2_report.Rda",
    package = "Reproducibility.in.Plant.Pathology",
    mustWork = TRUE
  )
)
```

@@

font_import()
```
``
